Something something

### 2024-08-29 paper/ms.tex
Add evol history results text

@@

>>>>

\subsection{Evolutionary History}\label{ssec:evol}

@@

In an effort towards understanding the events in our SOI's history that led to the behavior around the dashed line in Figure~\ref{fig:alpha}, we examine the evolution of some of its key quantities. In the upper panel of Figure~\ref{fig:history}, we show the SFH of our galaxy with the same dashed line as in Figure~\ref{fig:alpha} (at an age of $10.75\,\Gyr$ in that plot is at a time of $\sim3\,\Gyr$ here). This SFH is computed from the formation times of all star particles in the subhalo at $z=0$. This allows us to compute the SFH at fine time resolution, but also means contamination by accreted stellar debris. We see two peaks in the SFH at $t\sim2.5$ and $\sim4.5\,\Gyr$ of an amplitude of about $70$ and $60\,\Msunyr$. The dashed line corresponds to a relative drop in the SFR, down to about $10\,\Msunyr$ before quickly recovering.

The middle panel shows the accretion rate of the central black hole as a fraction of the maximum (Eddington) accretion rate. Early in its history ($t<2\,\Gyr$), the subhalo experiences high accretion rates. The accretion rate then steadily declines until $t\sim5\,\Gyr$ at which point it switches to the low accretion/radio mode. However, at the dashed line there is a localized peak in the accretion rate, maxing out at about $30\%$ Eddington.

The lower panel shows the virial mass of the subhalo, as measured by $M_{200}$ -- the mass within the radius that encloses a region of density $200\times$ the mean density of the universe. Early on at $t<4\,\Gyr$ the virial mass grows roughly linearly up to $\sim2\times10^{12}\,\Msun$. After that, the virial mass remains roughly constant until sharp increases at $t\sim10$ and $\sim12\,\Gyr$. The transition in the virial mass from linear to constant at $t\sim4\,\Gyr$ is followed $1\,\Gyr$ later by a sudden drop in the SFR and BH accretion rate.
